Deep Probabilistic Models for Camera Geo-Calibration

### 2018-07-19 chapters/introduction/introduction.tex
minor change

\subsection{Geo-Calibration}
In the camera pin-hole model, the projection from scene to the image
frame are determined by camera intrinsic and extrinsic parameters. 
The intrinsic parameters describe the information of camera
itself such as focal length, principal point \etc; 
The extrinsic parameters describe the external states of the
camera, such as the camera poses and translation under some
coordinate system.
Some applications like GIS and geo-localization are more interested in
calibrating the camera under geographic coordinates, namely knowing
the camera pose with respect to the ground reference frame (\ie ENU)
and camera location in geographic coordinates. We refer to such
calibration task as \textbf{geo-calibration}.

The complete geo-calibration includes intrinsic (focal
length, principal points \etc) and extrinsic parameters.
In this work, our study mainly focuses on estimating geo-calibration
extrinsic parameters like camera pose and the
geo-orientation/geo-localization of the camera.

>>>>

\subsection{Geo-Calibration}
Automatic image geo-calibration continues to grow in importance as a
direct result of the increasing amount of imagery available
via the Internet. Conceptually geo-calibration task is
straightforward: given an image, identify the location it was captured
in the world and the direction the camera was facing. Solving this
problem is of great value for a wide variety of fields, with potential
applications ranging from the forensic sciences~\cite{stylianou13jane}
to crowd-sourced environmental monitoring~\cite{zhang2012mining}.

Extracting location-dependent or orientation-dependent features from
image data has drawn a great detail of attention from the vision
community~\cite{jacobs07geolocate, jacobs11geolocate,
jacobs08geoorient}. The common trend amongst these methods is that
they take advantage of a large dataset of geo-referenced images. Hays
and Efros~\cite{hays2008im2gps} use a data-driven scene matching
approach to localize a query image using a large dataset of geo-tagged
images.  Doersch et al. extract location-dependent features that
capture the relative appearance differences of large cities.  Lin et
al.~\cite{lin2013cross} localize a ground-level image by learning the
relationship between pairs of ground and aerial images of the same
location. Other techniques focus on urban environments and infer
location using local image
descriptors~\cite{schindler2008detecting,snavely2006photo}. Li et
al.~\cite{li2012worldwide} exploit geo-registered 3D points clouds to
estimate camera pose. Many other cues exist, such as the
skyline~\cite{baatz2012large,ramalingam2009geolocalization}, sky
appearance~\cite{lalonde2010sun,workman2014rainbow}, and
shadows~\cite{junejo2008estimating,wu2010geo}.

However, recognizing the geo-location and geo-orientation of an
arbitrary outdoor image is an extremely challenging task.  Many
methods have been proposed; the most common approach is to build a
large database of images with known location and localize a query
image using either local~\cite{li2010location,schindler2008detecting}
or global~\cite{hays2008im2gps,doersch2012what} image features.  This
approach is not applicable when no nearby ground-level imagery exists
in the reference database, such as when the image was not captured
near a popular tourist destination.  Even when reference imagery is
available, the appearance of the objects may not be visually
distinctive, for example a train track or a body of water.

### 2018-07-19 chapters/introduction/junk.tex
minor change

>>>>

In the camera pin-hole model, the projection from scene to the image
frame are determined by the camera intrinsic and extrinsic parameters. 
The intrinsic parameters describe the information of camera
itself such as focal length, principal point \etc; 
The extrinsic parameters describe the external states of the
camera, such as the camera poses and translation under some
coordinate system.
Some applications like GIS and geo-localization are more interested in
calibrating the camera under geographic coordinates, namely knowing
the camera pose with respect to the ground reference frame (\ie ENU)
and camera location in geographic coordinates. We refer to such
calibration task as \textbf{geo-calibration}.

The complete geo-calibration includes intrinsic (focal
length, principal points \etc) and extrinsic parameters.
In this work, our study mainly focuses on estimating geo-calibration
extrinsic parameters like camera pose and the
geo-orientation/geo-localization of the camera.
